\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Sudipta Sen} \\ \vspace{1pt}

    \small { \raisebox{-0.1\height}\faPhone\ \underline{+91-8240824188} ~} \href{mailto:yourname@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sensudipta779@gmail.com}} ~ 
    \href{https://linkedin.com/in/sudipta-sen-10127a170}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{linkedin.com/in/sudipta-sen-10127a170}}  ~
    \href{https://leetcode.com/sudipta1495}{\raisebox{-0.2\height}\faPoll\ \underline{leetcode.com/sudipta1495}}
    \vspace{-7pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Allahabad}{Sept 2021 -- May 2023}
      {MTech in Information Technology - \textbf{CGPA} - \textbf{9.32/10}}{Prayagraj, U.P}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Calcutta}{Oct 2017 -- July 2020}
      {Masters in Computer Application - \textbf{Percentage} - \textbf{85.6\%}}{Kolkata, W.B}
  \resumeSubHeadingListEnd
\vspace{-20pt}
\section{EXPERIENCE}

	\resumeSubHeadingListStart

	\resumeSubheading
      {Indian Institute of Information Technology Allahabad}{Prayagraj, U.P}
      {\underline{Undergraduate Teaching Assistant}}{Oct 2021 -- Present}
      \begin{enumerate}
		\item Assisting instructors in managing development and evaluation of course assignments.
		\item Providing the professor with feedback related to student performance.
	  \end{enumerate}
    \resumeSubheading
      {Alumnus Software Limited}{Kolkata, W.B}
      {\underline{Member of Technical Staff Grade I}}{Feb 2021 -- Sept 2021}
      \begin{enumerate}
      
      \item ATM bonding asymmetric line rate test automation framework development.\newline\textbf{Achievement:} Manual effort of 1 day reduced to less than 3 hours with no manual error.

      \item SoC power managment validation.
      Design automated test cases for power and thermal management of CPU.
      \end{enumerate}
      

		

\vspace{-20pt}
	  \resumeSubheading  
      {}{}
      {\underline{Trainee Engineer}}{Aug 2020 -- Jan 2021}
	   %-----------------------------
	   \begin{enumerate}
      	\item Automation of power imbalance forecasting and account profitability analyses using PowerApps and PowerBI.
      \item Pass and failed log analyser using python.
	     \end{enumerate}
\vspace{10pt}
  \resumeSubHeadingListEnd
  
%------RELEVANT COURSEWORK-------
\vspace{-40pt}
\section{TECHNICAL SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Data Structures \& Algorithms
                \item Operating Systems
                \item Computer Network
                \item Database Management System (DBMS)
                \item C++
                \item Python
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

\vspace{-10pt}
\section{PROJECT}
\begin{itemize}
\item \textbf{Path Planning Using Deep Reinforcement Learning for Mobile Robot:} Proximal policy optimization algorithm is used to make the robot learn to find path in a known environment. There are obstacles in the environment and the agent's task is to avoid the obstacles and reach the destination successfully. 
{\href{https://github.com/Sudipta-Sen/Path_Planning_DRL }{\raisebox{-0.1\height}\faExternalLink }}
%\end{itemize}
%\begin{itemize}
\item \textbf{Question Pair similarity:} Duplication of questions is one of the many issues that Q\&A platforms like Quora and Stack Overflow confront. Various types of machine learning models are used for comparison. Those are logistic regression, naive bayes, decision tree, random forest, gradient boosting algorithm.

\end{itemize}

%-----------PROJECTS-----------
\vspace{-20pt}
\section{PUBLICATION}
\begin{itemize}
\item \textbf{Recommendation of Influenced Products Using Association Rule Mining: Neo4j as a Case Study:} In this paper the recommendation system has been built based on association rule mining. The entire framework has been developed in Neo4j graph data model {\href{https://link.springer.com/article/10.1007/s42979-021-00460-8}{\raisebox{-0.1\height}\faExternalLink }}
\end{itemize}
    
 
 %-----------CERTIFICATIONS---------------
 \vspace{-30pt}
\section{ACHIEVEMENT}
\begin{itemize} 
\item Qualify UGC-NET for eligibility for Assistant Professor on 4th December, 2019 in subject Computer Science and Applications.
\end{itemize} 

\vspace{-35pt}
\section{PERSONAL SKILLS}
	%\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=1pt]
                \item Team Player
                \item Quick Learner
                \item Positive Attitude
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

\vspace{-10pt}
\section{PERSONAL DETAILS}
\begin{itemize} 
\item \textbf{Date of Birth:} 14th July, 1995
\vspace{-10pt}
\item \textbf{languages known: } English, Hindi, Bengali
\end{itemize} 

\end{document}
© 2022 Overleaf English|Privacy and TermsSecurityContact UsAboutBlogOverleaf on TwitterOverleaf on FacebookOverleaf on LinkedIn
